Semantic integration of physiology phenotypes: an application to the cellular phenotype ontology

### 2012-01-19 paper/drinking-with-figs.tex

\documentclass{bioinfo}
\usepackage{setspace}

\copyrightyear{2005}
\pubyear{2005}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{multirow}
\usepackage{pifont}
% Load packages
\usepackage{cite} % Make references as [1-4], not [1,2,3,4]
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage[utf8]{inputenc} %unicode support
\urlstyle{rm}
\usepackage{natbib}
\renewcommand{\cite}{\citep}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\begin{document}
\firstpage{1}

@@

\author{Robert Hoehndorf$^1$ and Midori
  A. Harris$^2$ and Heinrich Herre$^3$ and Gabriella Rustici$^4$ and
  Georgios V. Gkoutos$^{1}$}

\address{$^{1}$Department of Genetics, University of Cambridge,
  Downing Street, Cambridge, Cambridge CB2 3EH, UK\\
  $^{2}$Department of Biochemistry; University of Cambridge, 80 Tennis
  Court Road, Cambridge CB2 1GA, UK\\
  $^{3}$Institute for Medical Informatics, Statistics and
  Epidemiology, University of Leipzig, Haertelstrasse 16-18, 04107
  Leipzig, Germany\\
  $^{4}$European Bioinformatics Institute, Wellcome Trust Genome
  Campus, Hinxton, Cambridge, Cambridge CB10 1SD, UK}

@@

\begin{table*}
  \centering
  \begin{tabular}{l|l|l|l}
    & Increased cytoplasmic flow rate & Normal cytoplasmic flow rate & Decreased
    cytoplasmic flow rate \\
    \hline
    Increased frequency &increased total flow rate &increased total
    flow rate &?\\
    Normal frequency &increased total flow rate &normal total flow
    rate &decreased total flow rate\\
    Decreased frequency &?&decreased total flow rate &decreased total
    flow rate\\
    \hline
  \end{tabular}
  \caption{\label{tbl:flow}Interdependency for the attribute {\em
      Total cytoplasmic flow rate}. A {\em Total cytoplasmic flow
      rate} is an attribute of {\em Regulation of cytoplasmic
      streaming} processes, while {\em Cytoplasmic flow rate} is an
    attribute of individual {\em cytoplasmic streaming}
    processes. Depending both on whether the cytoplasmic flow rate in
    individual {\em cytoplasmic streaming} processes is increased or
    decreased and whether the frequency of occurrence of {\em
      cytoplasmic streaming} is increased or decreased, the total
    cytoplasmic flow rate can be increased or decreased.}
\end{table*}

@@

\bibliographystyle{plain} % Style BST file
\bibliography{lc}

>>>>

\documentclass[12pt]{article}
\usepackage{times}
\usepackage{setspace}
\doublespacing

%\copyrightyear{2005}
%\pubyear{2005}
\usepackage{graphicx}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{multirow}
\usepackage{pifont}
% Load packages
\usepackage{cite} % Make references as [1-4], not [1,2,3,4]
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage[utf8]{inputenc} %unicode support
\urlstyle{rm}
\usepackage{natbib}
\renewcommand{\cite}{\citep}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\begin{document}
%\firstpage{1}

@@

\author{Robert Hoehndorf$^1$ and Midori
  A. Harris$^2$ and\\Heinrich Herre$^3$ and Gabriella Rustici$^4$ and
  Georgios V. Gkoutos$^{1}$}

\date{$^{1}$Department of Genetics, University of Cambridge,
  Downing Street, Cambridge, Cambridge CB2 3EH, UK\\
  $^{2}$Department of Biochemistry; University of Cambridge, 80 Tennis
  Court Road, Cambridge CB2 1GA, UK\\
  $^{3}$Institute for Medical Informatics, Statistics and
  Epidemiology, University of Leipzig, Haertelstrasse 16-18, 04107
  Leipzig, Germany\\
  $^{4}$European Bioinformatics Institute, Wellcome Trust Genome
  Campus, Hinxton, Cambridge, Cambridge CB10 1SD, UK}

@@

\begin{table*}
  \centering
  \begin{tabular}{p{2cm}|p{4cm}|p{4cm}|p{4cm}}
    & Increased cytoplasmic flow rate & Normal cytoplasmic flow rate & Decreased
    cytoplasmic flow rate \\
    \hline
    Increased frequency &increased total flow rate &increased total
    flow rate &?\\
    Normal frequency &increased total flow rate &normal total flow
    rate &decreased total flow rate\\
    Decreased frequency &?&decreased total flow rate &decreased total
    flow rate\\
    \hline
  \end{tabular}
  \caption{\label{tbl:flow}Interdependency for the attribute {\em
      Total cytoplasmic flow rate}. A {\em Total cytoplasmic flow
      rate} is an attribute of {\em Regulation of cytoplasmic
      streaming} processes, while {\em Cytoplasmic flow rate} is an
    attribute of individual {\em cytoplasmic streaming}
    processes. Depending both on whether the cytoplasmic flow rate in
    individual {\em cytoplasmic streaming} processes is increased or
    decreased and whether the frequency of occurrence of {\em
      cytoplasmic streaming} is increased or decreased, the total
    cytoplasmic flow rate can be increased or decreased.}
\end{table*}

@@

\bibliographystyle{natbib} % Style BST file
\bibliography{lc}

\clearpage

\section*{Figure legends}
\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{onto.pdf}
  \caption{Overview over basic top-level categories. Physical objects
    are entities that are wholly present at time points. Qualities are
    attributes of entities. Functions are capabilities that arise from
    physical objects with their qualities, and processes are
    temporally extended entities that may be realizations of a
    function.\label{fig:onto}}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{processpatterns.pdf}

\begin{figure*}
  \centering
  \includegraphics[width=1.2\textwidth, height=.4\textheight, angle=270]{overview.pdf}
  \caption{Overview over the taxonomic structure of CPO. The structure
    is based on a cellular component class $X$ and the cellular
    processes $P(X)$ in which $X$ is involved.\label{fig:overview}}
\end{figure*}
